### 2018-07-09 article.tex
Results.

\begin{itemize}
	\item \emph{Gaussian Naive Bayes} (\textsc{gnb}) \citep{gnb},
	\item \emph{k-Nearest Neighbors} (k\textsc{nn}) --- with \oldstylenums{5} neighbors and \emph{Minkowski} metric,
	\item \emph{Decision Tree Classifier} (\textsc{dtc}) --- with \emph{Gini} criterion \citep{loh2011classification}.
\end{itemize}

@@

\begin{sidewaystable}
	\restable{kNN}{k\textsc{nn}}
\end{sidewaystable}

@@

>>>>

\begin{itemize}
	\item \emph{Gaussian Naive Bayes} (\textsc{gnb}) \citep{gnb},
	%\item \emph{k-Nearest Neighbors} (k\textsc{nn}) --- with \oldstylenums{5} neighbors and \emph{Minkowski} metric,
	\item \emph{Decision Tree Classifier} (\textsc{dtc}) --- with \emph{Gini} criterion \citep{loh2011classification}.
\end{itemize}

@@

%\begin{sidewaystable}
%	\restable{kNN}{k\textsc{nn}}
%\end{sidewaystable}

@@

\begin{table}[!h]
%\vspace{-.5em}
\centering
\centering
\setlength{\tabcolsep}{3.5pt}
\def\arraystretch{1.1}
\begin{tabular}{@{}|c|ccc|cc|cc|ccccc|@{}}\hline%
clf & full & us & os & notos & wos & nopru & wpru & reg & wei & con & nor & nci\\\hline

%\multirow{2}{*}{\rotatebox[origin=c]{-90}{\bfseries \textsc{ir}}} &
%\multicolumn{3}{c|}{\bfseries Samples} &
%\multirow{2}{*}{\bfseries Features} &
%\multicolumn{1}{c|}{\multirow{2}{*}{\rotatebox[origin=c]{-90}{\bfseries DS}}}
%\\

%&
%\multicolumn{1}{c}{\textsc{all}} & 
%\multicolumn{1}{c}{\textsc{maj}} & 
%\multicolumn{1}{c|}{\textsc{min}} &
%&

%	\\\hline\hline

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{results/summary.csv}{}%
	{\clf &
	\full & \us & \os &
	\withoutos & \withos & 
	\withoutpru & \withpru &
	\reg & \wei & \con & \nor & \nci

	}%
\end{tabular}
\caption{NAZWIJŻE TABELĘ}\label{tab:summary}
\end{table}
